Bullet Groups as a test of $\Lambda$CDM

### 2014-03-05 paper/ms.tex
new figures

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{fig:configuration}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{
Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{New_figures/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and
  sub-structure (black circle) in the sample.}  
\label{fig:configuration}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
\end{center}
\caption{
Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}
